---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# futureScenario

<!-- badges: start -->
<!-- badges: end -->

The goal of futureScenario is to ...

## to do

1. Obtain and create useable GNAF data - **done**
2. Incorporate Graemes prediction workflow  
3. Generate reporting outputs  
4. Generate shiny apps

## Installation

<!--
You can install the released version of futureScenario from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("futureScenario")
```
-->

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Shaunson26/futureScenario")
```

```{r}
library(futureScenario)
```

## Data

A flattened and minified GNAF address dataset `?gnaf`

```{r}
head(gnaf)
```

## Functions

`return_address_coords()` is used to query `gnaf`. Currently with exact matches only.
If any query files are missing, there will be a wildcard used for that those fields

```{r}
# An exact match
return_address_coords(street_number = 2, street_name = 'IVY STREET', locality = 'DARLINGTON', postcode = '2008')

# missing street_name returns all street_names matching the rest of the query
return_address_coords(street_number = 2, locality = 'DARLINGTON', postcode = '2008')
```

## Shiny

Shiny apps for exploration and other purposes

```{r, eval = F}
run_gnaf_leaflet_shiny()
```




